### 2024-03-27 sections/4gluing_alt.tex
More work in section 4.

\begin{proposition}
    The functors $\falg(\catC)$ and $\lcfa(\catC)$ respect sequential colimits.
\end{proposition}

@@

    An object of the limit is a collection $(A_0, A_1, \dots)$ of factorization algebras on $M_0, M_1, \dots$, respectively, together with equivalences $\eta_i: A_i \simeq A_{i+1}|_{M_i}$ for $i \geq 0$. Towards showing essential surjectivity of $\alpha$ we will construct the factorization algebra $A$ on $M$ given by the following prescription. Given any open $U \subset M$, there will be an integer $i$, such that $U \subset M_i$; we take the smallest such integer, call it $i_U$, and define
    %
    \begin{equation}
        A(U) := A_{i_U} (U).
    \end{equation}
    %
    Given a morphism $U \xhookrightarrow{} V$ we know that $i_U \leq i_V$, and the morphism we assign is
    %
    \begin{equation}
        A(U \xhookrightarrow{} V) := A_{i_U}(U) \xrightarrow{\eta_{i_U}(U)} \cdots \xrightarrow{\eta_{i_V - 1}(U)} A_{i_V} (U) \xrightarrow{A_{i_V} (U \xhookrightarrow{} V)} A_{i_V} (V).
    \end{equation}

    ...

    Using \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg}, we will take the disk algebra incarnation of the relevant $\infty$-categories.
\end{proof}

\begin{proposition}
    {\color{red} (Probably untrue)} Factorization algebras can be formulated as functors
    %
    \begin{equation}
        \falg_{-}(\catC), \lcfa_{-}(\catC): \mfld \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
    \end{equation}
\end{proposition}

\begin{proof}
    The proof will go along the same lines for both, so we will focus on factorization algebras, and shorten notation to $\mathscr{F} := \falg (\catC): \mfld[r] \xrightarrow{} \cat^{\mathsf{op}}$. Beyond the obvious assignment on objects, to define the functor we need to provide a map of spaces
    %
    \begin{equation}
        \mathsf{Hom}_{\mfld}(M, N) \xrightarrow{\ \ \eta \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}.
    \end{equation}
    %
    This data can be provided in the form of a map of simplicial sets, whose components are
    %
    \begin{equation}
        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}_p,
    \end{equation}
    %
    where the morphism space notation was introduced in \Cref{def:mfld_infty_cat}. Any map from a space will factor through the maximal $\infty$-groupoid of the codomain, so that we can drop the $^{\simeq}$ requirement. Unraveling the definition of a functor category at the same time means that we need to provide maps
    %
    \begin{equation}
        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Hom}_{\mathsf{sSet}}(\mathscr{F}(N) \times \Delta^p, \mathscr{F}(M)).
    \end{equation}
    %
    And indeed,
    %
    \begin{align}
        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xhookrightarrow{\ \ \ \ \ \ \ }& \mathsf{Emb}(M \times \Delta^p, N \times \Delta^p) \\
        \xrightarrow{\mathrm{restrict}}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p), \mathscr{F}(M \times \Delta^p)) \\
        \xrightarrow{\ \pi_{1*} \circ -}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p) , \mathscr{F}(M)) \\
        \xrightarrow{\ - \circ \alpha^p \ }& \mathsf{Hom_{sSet}} (\mathscr{F}(N) \times \Delta^p , \mathscr{F}(M)).
    \end{align}
    %
    Let us further describe the final arrow. It arises as a functor
    %
    \begin{equation}
        \mathscr{F} (N) \times \Delta^p \xrightarrow{\ \ \alpha^p \ \ } \mathscr{F}(N \times \Delta^p),
    \end{equation}
    %
    whose components are given by
    %
    \begin{equation}
        \alpha^p_m: \mathscr{F} (N)_m \times \mathsf{Hom}_{\Delta}([m], [p]) \xrightarrow{} \mathscr{F}(N \times \Delta^p)_m.
    \end{equation}
    %
    ......
\end{proof}

{\color{red} Work in progress}

This perspective on the theory of locally constant factorization algebras as a functor reframes the gluing result \Cref{thm:gluing_lcfas}, and together with lemma \Cref{lem:disk/M_to_disk} points towards a result like the following:

@@

>>>>

\begin{proposition}\label{prop:fa_seq_col}
    The functors $\falg(\catC)$ and $\lcfa(\catC)$ respect sequential colimits.
\end{proposition}

@@

    An object of the limit is a collection $(A_0, A_1, \dots)$ of factorization algebras on $M_0, M_1, \dots$, respectively, together with equivalences $\eta_i: A_i \simeq A_{i+1}|_{M_i}$ for $i \geq 0$. Towards showing essential surjectivity of $\alpha$ we will construct the factorization algebra $A$ on $M$ given by the following prescription. Using \Cref{cor:disk_alg=falg}, we will take the disk algebra incarnation of the relevant $\infty$-categories, so that we want to construct $A \in \alg{\disk[r]_{/M}}$. Given any disk $U \subset M$, there will be an integer $i$, such that $U \subset M_i$; we take the smallest such integer, call it $i_U$, and define
    %
    \begin{equation}
        A(U) := A_{i_U} (U).
    \end{equation}
    %
    Given a morphism $U \xhookrightarrow{} V$ we know that $i_U \leq i_V$, and the morphism we assign is
    %
    \begin{equation}\label{eq:seq_col_gluing}
        A(U \xhookrightarrow{} V) := \left( A_{i_U}(U) \xrightarrow{\eta_{i_U}(U)} \cdots \xrightarrow{\eta_{i_V - 1}(U)} A_{i_V} (U) \xrightarrow{A_{i_V} (U \xhookrightarrow{} V)} A_{i_V} (V) \right).
    \end{equation}
    %
    The same construction works for multimorphisms too, e.g. for $U \sqcup U' \xhookrightarrow{} V$ we would have
    %
    \begin{align}
        A(U \sqcup U' \xhookrightarrow{} V) := \left( A_{i_U}(U) \otimes A_{i_{U'}} (U') \xrightarrow{\eta_{i_U}(U) \otimes \mathbb{1}} \cdots \xrightarrow{\eta_{i_V - 1}(U) \otimes \mathbb{1}} A_{i_V} (U) \otimes A_{i_{U'}}(U') \right. \notag\\
        \left.\xrightarrow{\mathbb{1} \otimes \eta_{i_{U'}}(U')} \cdots \xrightarrow{\mathbb{1} \otimes \eta_{i_V - 1}(U')} A_{i_V} (U) \otimes A_{i_V} (U') \xrightarrow{} A_{i_V} (U \sqcup U') \xrightarrow{A_{i_V} (U \sqcup U' \xhookrightarrow{} V)} A_{i_V} (V) \right).
    \end{align} 
    %
    This describes the data of a $\disk[r]_{/M}$-algebra. When applying the above construction to locally constant factorization algebras it's also clear that the property of local constancy is inherited since then all the arrows in \cref{eq:seq_col_gluing} are equivalences.

    To show essential surjectivity of $\alpha$ we need to find equivalences $\epsilon_i: A|_{M_i} \xrightarrow{\simeq} A_i$ for all $i \geq 0$, which fit into a commutative diagram
    %
    \begin{equation}\label{cd:seq_col_equivs}
        \begin{tikzcd}
            & A|_{M_i} = (A|_{M_{i+1}})|_{M_i} \arrow[ld, "\epsilon_i"'] \arrow[rd, "\epsilon_i|_{M_i}"] & \\
            A_i \arrow[rr, "\eta_i"] & & A_{i+1}|_{M_i},
        \end{tikzcd}
    \end{equation}
    %
    where we have remembered that consecutive restrictions commute on the nose. The equivalence $\epsilon_i$ is given by its components $\epsilon_i(U): A|_{M_i} \xrightarrow{} A_i(U)$, which we define as
    %
    \begin{equation}
        \epsilon_i(U) := \left( A|_{M_i}(U) = A_{i_U}(U) \xrightarrow{\eta_{i_U}(U)} \cdots \xrightarrow{\eta_{i-1}(U)} A_i (U) \right).
    \end{equation}
    %
    That these assemble into a natural transformation is provided by commutative diagrams like
    %
    \begin{equation}
        \begin{tikzcd}[column sep = {2.5cm}]
            A_{i_U}(U) \arrow[d, "\eta_{i_V-1}(U) \circ \cdots \circ \eta_{i_U}(U)"'] \arrow[r, "\eta_{i-1}(U) \circ \cdots \circ \eta_{i_U}(U)"] & A_i(U) \arrow[d, "="] \\
            A_{i_V}(U) \arrow[d] \arrow[r, "\eta_{i-1}(U) \circ \cdots \circ \eta_{i_V}(U)"] & A_i (U) \arrow[d] \\
            A_{i_V}(V) \arrow[r, "\eta_{i-1}(V) \circ \cdots \circ \eta_{i_V}(V)"] & A_i (V).
        \end{tikzcd}
    \end{equation}
    %
    That these equivalences $\epsilon_i$ fit into diagrams like in \cref{cd:seq_col_equivs} is obvious from their definition.

    Showing full faithfulness of $\alpha$ is the same for ordinary and locally constant factorization algebras since the later are a full $\infty$-subcategory of the former. What we have to show is that
    %
    \begin{equation}
        \mathsf{Hom}_{\mathscr{F} (M)}(A, B) \xrightarrow{\ \ \alpha \ \ } \mathsf{Hom}_{\mathsf{lim}} (\alpha (A), \alpha(B)) \simeq \mathsf{lim}_{i \geq 0} (\mathsf{Hom}_{\mathscr{F}(M_i)} (A_i, B_i))
    \end{equation}
    %
    is an equivalence of spaces. In the last equivalence we made use of the essential surjectivity from above. The same idea as for the construction of $A$ work here too, the main point being that any disk $U$ will have a finite $i_U$.

    ...
\end{proof}

Considering \Cref{thm:decom_strat_man} together with the statements of \Cref{cor:disk_alg=falg} (or \Cref{thm:disk_alg=lcfa} in the locally constant case), together with the above \Cref{prop:fa_seq_col}, we have an algorithm of how to compute the $\infty$-category of factorization algebras on any manifold if we know it on the basics. In other words, the theory of (locally constant) factorization algebras is fully determined by the assignment
%
\begin{equation}
    U \mapsto \falg_U (\catC),
\end{equation}
%
for each basic $U \in \bsc$.

After a simplification down to disks, in the locally constant case , lemma \Cref{lem:disk/M_to_disk} points towards a result like the following:

@@

%\begin{proposition}
%    {\color{red} (Probably untrue)} Factorization algebras can be formulated as functors
%    %
%    \begin{equation}
%        \lcfa_{-}(\catC): \mfld \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
%    \end{equation}
%\end{proposition}

%\begin{proof}
%    The proof will go along the same lines for both, so we will focus on factorization algebras, and shorten notation to $\mathscr{F} := \falg (\catC): \mfld[r] \xrightarrow{} \cat^{\mathsf{op}}$. Beyond the obvious assignment on objects, to define the functor we need to provide a map of spaces
%    %
%    \begin{equation}
%        \mathsf{Hom}_{\mfld}(M, N) \xrightarrow{\ \ \eta \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}.
%    \end{equation}
%    %
%    This data can be provided in the form of a map of simplicial sets, whose components are
%    %
%    \begin{equation}
%        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}_p,
%    \end{equation}
%    %
%    where the morphism space notation was introduced in \Cref{def:mfld_infty_cat}. Any map from a space will factor through the maximal $\infty$-groupoid of the codomain, so that we can drop the $^{\simeq}$ requirement. Unraveling the definition of a functor category at the same time means that we need to provide maps
%    %
%    \begin{equation}
%        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Hom}_{\mathsf{sSet}}(\mathscr{F}(N) \times \Delta^p, \mathscr{F}(M)).
%    \end{equation}
%    %
%    And indeed,
%    %
%    \begin{align}
%        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xhookrightarrow{\ \ \ \ \ \ \ }& \mathsf{Emb}(M \times \Delta^p, N \times \Delta^p) \\
%        \xrightarrow{\mathrm{restrict}}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p), \mathscr{F}(M \times \Delta^p)) \\
%        \xrightarrow{\ \pi_{1*} \circ -}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p) , \mathscr{F}(M)) \\
%        \xrightarrow{\ - \circ \alpha^p \ }& \mathsf{Hom_{sSet}} (\mathscr{F}(N) \times \Delta^p , \mathscr{F}(M)).
%    \end{align}
%    %
%    Let us further describe the final arrow. It arises as a functor
%    %
%    \begin{equation}
%        \mathscr{F} (N) \times \Delta^p \xrightarrow{\ \ \alpha^p \ \ } \mathscr{F}(N \times \Delta^p),
%    \end{equation}
%    %
%    whose components are given by
%    %
%    \begin{equation}
%        \alpha^p_m: \mathscr{F} (N)_m \times \mathsf{Hom}_{\Delta}([m], [p]) \xrightarrow{} \mathscr{F}(N \times \Delta^p)_m.
%    \end{equation}
%    %
%    ......
%\end{proof}
